A Novel Sampling Method Using Stochastic Gradient Descent

### 2016-12-07 paper/main.tex
minor clean

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest (> 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
\caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
\caption{$d(k)$, difference between the empirical pdf and the expected pdf for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_4}
\end{figure}
As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4= 1))$ is much longer than any single mode distribution. Its convergence time is also the longest.

% section upper_bound_on_the_mixing_time (end)

% ===================================================================================
\section{Discussion} % (fold)
\label{sec:discussion}

@@

% section discussion (end)
\newpage
% ===================================================================================
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Section in Appendix}
\label{appendix-sec1}

Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
Sample text.

>>>>

\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). It can be seen that $d(k)$ decreases exponentially for all of the functions. And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right). For $\exp(-|x|)$, it has not converge to the true pdf yet. For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
\end{figure}
As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest ($>$ 100) and the mixing time of $\exp(-|x|^4)$ is the shortest. This is coherent with their convergence time. For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.

\begin{table}[h!]
\centering
\begin{tabular}{ll}
\hline
Density & Median convergence time \\
\hline
1        & 164\\
2        & 144\\
3        & 138\\
4        & 129\\
5        & 21480\\
\hline
\end{tabular}
\caption{Median convergence time of the five target densities}
\label{tbl:med_conv_time}
\end{table}

\begin{figure}
\centering
% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
\caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
\end{figure}

\begin{figure}
\centering
% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
\caption{$d(k)$, difference between the empirical pdf and the expected pdf for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_4}
\end{figure}
As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4 - 1))$ is much longer than any single mode distribution. Its convergence time is also the longest.

% section upper_bound_on_the_mixing_time (end)
\newpage
% ===================================================================================
\section{Discussion} % (fold)
\label{sec:discussion}

@@

% section discussion (end)
% \newpage
% ===================================================================================
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
% \appendix

% \section{Section in Appendix}
% \label{appendix-sec1}

% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
% Sample text.
